resevol: an R package for spatially explicit models of pesticide resistance

### 2022-07-30 notebook/ms/ms.Rmd
Update the website with the manuscript information, which will serve as the main vignette of the package from now on. The next step is to update the second vignette and create a third (which will be supporting information)

---
title: 'resevol: an R package for spatially explicit models of pesticide resistance
  given evolving pest genomes'
author: |
  | A. Bradley Duthie&#xb9;&#xb2;, et al.
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2]  alexander.duthie@stir.ac.uk, Biological and Environmental Sciences 3A149
  University of Stirling Stirling, FK9 4LA, UK'
output:
  word_document: default
  pdf_document:
    toc: no
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    toc: no
  html_document: default
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{RESEVOL, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: resevol.bib
biblio-style: apalike
---

@@

Finally, evolving and covarying traits can be used in place of fixed parameters described in pest ecology.
This is done by substituting `"Tj"` as an argument input in place of a numeric value, where `j` represents the trait number.
For example, the argument `move_distance = "T1"` will make Trait 1 the movement distance for individuals. 
The argument `food_consume = c("T2", "T3")` will set Traits 2 and 3 to define the amount of food of types 1 and 2 that can be consumed by a pest, respectively.
Parameters that can be replaced with evolving traits include `move_distance`, `food_needed_surv`, `pesticide_tolerated_surv`, `food_needed_repr`, `pesticide_tolerated_repr`, `mating_distance`, `lambda_value`, `movement_bouts`, `metabolism`, `food_consume`, and `pesticide_consume`.
The resevol package can thereby simulate agricultural pests with complex and co-evolving traits, and potentially evolving trait covariances, under a range of possible pest life histories.

@@

```{r, eval = TRUE}
sim <- run_farm_sim(mine_output = new_network, repro = "asexual", 
                    pesticide_number = 2, pesticide_init = "random", 
                    pesticide_consume = c("T1", "T2"), farms = 9,
                    pesticide_rotation_time = 16, pesticide_rotation_type = 3,
                    pesticide_tolerated_surv = 0, pesticide_per_cell = 1,
                    crop_rotation_time = 16, crop_number = 1, crop_per_cell = 4, 
                    food_consume = 1, reproduction_type = "food_based", 
                    food_needed_surv = 1, food_needed_repr = 1, max_age = 4, 
                    min_age_feed = 0, max_age_feed = 2, min_age_move = 3, 
                    max_age_move = 4, min_age_reproduce = 4, print_gens = FALSE,
                    max_age_reproduce = 4, age_pesticide_threshold = 2, 
                    rand_age = TRUE, move_distance = 2, immigration_rate = 10, 
                    time_steps = 160, print_last = TRUE, xdim = 64, ydim = 64);
```

@@

     ylab = "Mean pesticide consumed", cex.lab = 1, ylim = c(0, 0.35),

@@

legend(x = 158, y = 0.35, col = c("black", "red"), lty = c("solid", "dashed"),

@@

text(x = 5, y = 0.32, labels = "b", cex = 2);

@@

     ylab = "Mean trait value", cex.lab = 1, ylim = c(-0.9, 0),

@@

axis(side = 2, at = c(-0.8, -0.6, -0.4, -0.2), cex.axis = 1);

@@

legend(x = 158, y = 0, col = c("black", "red"), lty = c("solid", "dashed"),

>>>>

---
title: 'resevol: an R package for spatially explicit models of pesticide resistance
  given evolving pest genomes'
author: |
  | A. Bradley Duthie&#xb9;&#xb2;, et al.
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2]  alexander.duthie@stir.ac.uk, Biological and Environmental Sciences 3A149
  University of Stirling Stirling, FK9 4LA, UK'
output:
  word_document:
    reference_docx: docx_template.docx
  pdf_document:
    toc: no
  html_document: default
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    toc: no
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{RESEVOL, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: resevol.bib
biblio-style: apalike
---

@@

Finally, evolving and covarying traits can be used in place of fixed parameters described in pest ecology.
This is done by substituting `"Tj"` as an argument input in place of a numeric value, where `j` represents the trait number.
For example, the argument `move_distance = "T1"` will make Trait 1 the movement distance for individuals. 
The argument `food_consume = c("T2", "T3")` will set Traits 2 and 3 to define the amount of food of types 1 and 2 that can be consumed by a pest, respectively.
Up to 10 of the following parameters can be replaced with evolving traits: `move_distance`, `food_needed_surv`, `pesticide_tolerated_surv`, `food_needed_repr`, `pesticide_tolerated_repr`, `mating_distance`, `lambda_value`, `movement_bouts`, `metabolism`, `food_consume`, and `pesticide_consume`.
Mean values of traits can be set using the argument `trait_means`, which accepts a vector of the same length as the number of evolving traits such that indices correspond to trait numbers.
The resevol package can thereby simulate agricultural pests with complex and co-evolving traits, and potentially evolving trait covariances, under a range of possible pest life histories.

@@

```{r, eval = TRUE}
sim <- run_farm_sim(mine_output = new_network, repro = "asexual", 
                    pesticide_number = 2, pesticide_init = "random", 
                    pesticide_consume = c("T1", "T2"), farms = 9,
                    pesticide_rotation_time = 16, pesticide_rotation_type = 3,
                    pesticide_tolerated_surv = 0, pesticide_per_cell = 1,
                    crop_rotation_time = 16, crop_number = 1, crop_per_cell = 4, 
                    food_consume = 1, reproduction_type = "food_based", 
                    food_needed_surv = 1, food_needed_repr = 1, max_age = 4, 
                    min_age_feed = 0, max_age_feed = 2, min_age_move = 3, 
                    max_age_move = 4, min_age_reproduce = 4, print_gens = FALSE,
                    max_age_reproduce = 4, age_pesticide_threshold = 2, 
                    rand_age = TRUE, move_distance = 2, immigration_rate = 10, 
                    time_steps = 160, print_last = TRUE, xdim = 64, ydim = 64,
                    trait_means = c(0.1, 0.1));
```

@@

     ylab = "Mean pesticide consumed", cex.lab = 1, ylim = c(0, 0.4),

@@

legend(x = 158, y = 0.4, col = c("black", "red"), lty = c("solid", "dashed"),

@@

text(x = 5, y = 0.37, labels = "b", cex = 2);

@@

     ylab = "Mean trait value", cex.lab = 1, ylim = c(-0.9, 0.1),

@@

axis(side = 2, at = c(-0.8, -0.6, -0.4, -0.2, 0.0), cex.axis = 1);

@@

legend(x = 158, y = 0.1, col = c("black", "red"), lty = c("solid", "dashed"),
